Algebraic File Synchronization: Adequacy and Completeness

### 2016-11-02 p2/ordering.tex
Continue with update detection (ordering)

@@

Next, we prove that if $T\in\orderset{S}$, then $T\equiv S$.
We proceed by induction.
Our base cases are $\emptyseq$, where $\orderset{\emptyseq}=\{\emptyseq\}$,
and one-long sequences, where this is trivially true.
In our induction step we assume that $T^*\in\orderset{S^*}\Rightarrow T^*\equiv S^*$ holds
for all sequences of length $i\geq 1$ or less.

Let us consider $T\in\orderset{S}$ where $T$ and $S$ are of length $i+1$.
We know that due to \cref{ax_separate_commute,incomparable_is_independent}
$T$ can be rearranged into $T'\equiv T$ where
$T'=T_1\cc T_2\cc \cdots \cc T_k$ and the segments $T_j$ are pairwise independent,
and where we have the maximum number of segments possible.
$S$ can be converted similarly into $S'$, and
as because of \cref{equiv_simple_same_commands} $S$ and $T$ contain the same commands,
the segments of $S'$ will contain the same commands as those of $T$.
Let us therefore rearrange the segments of $S'$ so that the first segment
$S_1$ would correspond to (i.e. contain the same commands as) $T_1$, the second segment $S_2$ to $T_2$,
and so on.

@@

The remaining case is when $T'$ has at least two commands,
but only one segment, which means
that all nodes that the commands in $T'$ apply to
are related via $\descendant$.
$T'$ contains the same commands as $S$, and
from \cref{connected_changes} we see that the nodes the commands apply to therefore form a tree in $\setn$.
We can therefore select the command on the topmost node (let it be $\cxynv$),
and we know $T'$ contains commands on some of its child nodes.
Let one of these be $\czwmv$.
Now mark the command $\czwmv$ and all commands in $T'$ that are applied to nodes that are descendants of $m$.
From \cref{ax_separate_commute} we know that all remaining commands in $T'$ (except $\cxynv$)
commute with the marked commands; therefore we can swap them to get $T''\equiv T'$
where marked commands are next to $\cxynv$:
\[ T'' = T_\mathrm{unmarked\ left} \cc T_\mathrm{marked\ left} \cc \cxynv \cc T_\mathrm{marked\ right} \cc T_\mathrm{unmarked\ right}. \]

>>>>

% TODO delete unused results

@@

Next, we prove that if $T\in\orderset{S}$, then $T\equiv S$.
We proceed by induction on the length of $S$.
Our base cases are $\emptyseq$, where $\orderset{\emptyseq}=\{\emptyseq\}$,
and one-long sequences, where this is trivially true.
In our induction step we assume that $T^*\in\orderset{S^*}\Rightarrow T^*\equiv S^*$ holds
for all sequences of length $i\geq 1$ or less.

Let us consider $T\in\orderset{S}$ where $T$ and $S$ are of length $i+1$.
We know that due to \cref{ax_separate_commute,incomparable_is_independent}
$T$ can be rearranged into $T'\equiv T$ where
$T'=T_1\cc T_2\cc \cdots \cc T_k$ and the segments $T_j$ are pairwise independent,
and where we have the maximum number of segments possible.
$S$ can be converted similarly into $S'$, and
as $S$ and $T$ contain the same commands,
the segments of $S'$ will contain the same commands as those of $T'$.
Let us therefore rearrange the segments of $S'$ so that the first segment
$S_1$ would correspond to (i.e. contain the same commands as) $T_1$, the second segment $S_2$ to $T_2$,
and so on.

@@

The remaining case is when $T'$ has at least two commands,
but only one segment, which means
all nodes the commands in $T$ apply to are related via $\descendant$.
$T$ contains the same commands as $S$, and
from \cref{connected_changes} we see that the nodes the commands apply to form a tree in $\setn$.
We can therefore select the command on the topmost node (let it be $\cxynv$),
and we know $T$ contains commands on some of its child nodes.
Let one of these be $\czwmv$.
Now mark the command $\czwmv$ and all commands in $T$ that are applied to nodes that are descendants of $m$.
From \cref{ax_separate_commute} we know that all remaining commands in $T$ (except $\cxynv$)
commute with the marked commands; therefore we can swap them to get $T''\equiv T$
where marked commands are next to $\cxynv$:
\[ T'' = T_\mathrm{unmarked\ left} \cc T_\mathrm{marked\ left} \cc \cxynv \cc T_\mathrm{marked\ right} \cc T_\mathrm{unmarked\ right}. \]
